---
title: "copernicus"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Provides access simplified distribution of [ecopmo forecasts](https://github.com/BigelowLab/ecopmo) forecasts for *Calanus finmarchicus*.

## Requirements

  + [R v4.2+](https://www.r-project.org/)
  + [rlang](https://CRAN.R-project.org/package=rlang)
  + [ggplot2](https://CRAN.R-project.org/package=ggplot2)
  + [viridis](https://CRAN.R-project.org/package=viridis)
  + [sf](https://CRAN.R-project.org/package=sf)
  + [stars](https://CRAN.R-project.org/package=stars)
  + [yaml](https://CRAN.R-project.org/package=yaml)
  

## Installation

```
remotes::install_github("BigelowLab/calfinforecast")
```

## Daily refreshing

Each day the put is refreshed using 

`
$ Rscript /mnt/s1/projects/ecocast/corecode/R/ecopmo_forecast/calfinforecast/inst/scripts/copy_forecast.R
`

This copies the most recent forecasts (-5 days to +10 days, although that will vary by available forecast data.)  Makes a copy of the most recent configuration list, saves both a time-faceted forecast plot as well as per day forecast plots.


# Functions

Data are stored within the package, so we provide function to easily read these data.

## Rasters

Read the raw forecast data as raster,

```{r}
library(calfinforecast)
x = read_raster()
x
```

## Spatial cropping

Read in the convenience spatial bounding box.

```{r}
bb = get_bb(reg = "gom")
bb
```

## Configuration

The configuration list may provide important contextual information.

```{r}
cfg = read_config()
str(cfg)
```

## Graphics

Graphics can be composed of one time-facted plot or a collection of per-day plots.

```{r}
gg1 = plot_forecast(x, wrap = TRUE, crop = get_bb(reg = "gom"))
gg1
```
Alternatively we can retrieve a listing with one graphic per day.

```{r}
gg2 = plot_forecast(x, wrap = FALSE, crop = get_bb(reg = "gom"))
gg2[[6]]
```

## Images 

Each of these is renderded as a PNG.  You can list them...

```{r}
list_images("wrapped") |>
  base_name()
```

```{r}
list_images("daily") |>
  base_name()
```

